\TheTitle

### 2017-07-14 paper/background.tex
editing background

The repository events in the DAG are immutable; once a repository event
is created, it can't be changed. \dmg{the next sentences should be repository events, not commits}
Git allows operations to alter commits
and re-order them, but this will create a new commit with a new commit
hash.  This property makes a repository event unable to record the
traversal of merges into the master branch of the repository. A commit
cannot have references in the direction of the merge that merges the
commit, as this reference will change, requiring the commit to be
changed. \dmg{BE CONSISTENT, Git or git?} git provides
the command \verb|git log --children| which traverses
the DAG and prints the inverted edges relationship between events.

Under perfect conditions, visualizations of the DAG should show how a
repository changes over time; where logical branches are being made,
where merges are happening, and who is making the changes. Most
repositories are relatively simple, with
relatively few, small, branches with a clear, well defined
master branch. However, in large, active repositories it becomes very difficult for developers to use the DAG
to identify
the master branch, and as a consequence, where branches start and are merged back in their
way to master.

>>>>

The repository events in the DAG are immutable; once a repository event
is created, it can't be changed. \dmg{the next sentences should be
  repository events, not commits} Git allows operations to alter
repository events and re-order them, but this will create a new event
with a new commit hash. This property makes a repository event unable to
record the traversal of merges into the master branch of the repository.
Introducing an additional field to track the path to the master branch
would create a circular dependency between the parent and child. Any
updates to the DAG would modify the commit hashes for all repository
events in the repository. To alleviate this, git provides the command
\verb|git log --children| which traverses the DAG and prints the
inverted edges relationship between events.

Under perfect conditions, visualizations of the DAG show how a
repository changes over time; where logical branches are being made,
where merges are happening, and who is making the changes. Most
repositories are relatively simple, with relatively few, small, branches
with a clear, well defined master branch. However, in large, active
repositories it becomes very difficult for developers to use the DAG to
identify the master branch, and as a consequence, where branches start
and are merged on the path to the master branch. \evan{They do show in
  perfect conditions. If you don't have many branches, and you don't
  have any foxtrots, the first branch on the left of the DAG
  visualization WILL be the master branch}
